---
title: "R mark intro"
author: "Eugenia Pesci"
date: "2023-03-28"
output:
  pdf_document: default
  html_document: default
---
pdf_document – This creates a PDF file with LaTeX (an open source document layout system). If you don’t already have LaTeX, RStudio will automatically prompt you to install it.

word_document – This creates a Microsoft Word document (.docx).

odt_document – This creates an OpenDocument Text document (.odt).

rtf_document – This creates a Rich Text Format document (.rtf).  

md_document – This creates a Markdown document (which strictly conforms to the original Markdown specification)

github_document – This creates a GitHub document which is a customized version of a Markdown document designed for sharing on GitHub.

##Presentations
You can also use R Markdown to produce presentations. Automatically inserting the results of your R code into a presentation can save you lots of time. 

R Markdown renders files to specific presentation formats when you use the following output settings:

beamer_presentation – for PDF presentations with beamer

ioslides_presentation – for HTML presentations with ioslides

slidy_presentation – for HTML presentations with Slidy

powerpoint_presentation – for PowerPoint presentations

revealjs : : revealjs_presentation – for HTML presentations with reveal.js (a framework for creating HTML presentations that requires the reveal.js package)


## R Markdown

* HTML
* PDF
* MS Word documents.

When *you* click the **Knit** 

click here [link](http://rmarkdown.rstudio.com).
R Markdown see <http://rmarkdown.rstudio.com>.


<!--comment ![Plot this way](URL-picture) -->

`echo = FALSE`

```{r loading packages}
library(ggplot2)
library(palmerpenguins)
```


inside the text```{r} and ```

Win: ctrl+alt+i
Mac: command+option+i


## Visualizations
Here we will go through a series of visualizations

### Flipper and body mass in purple
Here, we plot flipper lenght against body mass

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point(color = 'purple')
```

